% scion-libp2p: Path-Aware Peer-to-Peer Content Delivery
% Target: ACM CoNEXT Workshop / IEEE INFOCOM Workshop
% Build: pdflatex main && bibtex main && pdflatex main && pdflatex main

\documentclass[sigconf,nonacm]{acmart}

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, calc, patterns}

% Remove ACM-specific metadata for workshop submission
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\begin{document}

\title{scion-libp2p: Path-Aware Peer-to-Peer Content Delivery\\with Epsilon-Greedy Path Selection}

\author{Eren Ari}
\affiliation{%
  \institution{Independent Research}
}
\email{erenari27@gmail.com}

\begin{abstract}
Standard peer-to-peer content delivery treats all network paths equally, ignoring path quality differences and causing congestion when peers greedily converge on the lowest-latency route. We present \textsc{scion-libp2p}, a path-aware P2P content overlay that combines continuous path probing with multi-armed bandit path selection, NDN-style in-network relay caching, cooperative cache coordination via Bloom filter exchange, and Reed-Solomon erasure coding for storage-efficient replication. Built on libp2p and inspired by SCION's end-host path control, our system probes direct and relay paths for RTT, jitter, hop count, and success rate, then applies configurable selection policies with controlled exploration to distribute load across viable paths. We implement and evaluate seven path selection strategies---epsilon-greedy, decaying-epsilon, UCB1, Thompson sampling, contextual bandits (LinUCB), greedy min-RTT, and random---across cluster sizes of 5 to 25 nodes with 100 requests per run. Fixed $\varepsilon$-greedy is the most scale-stable policy: P95 latency degrades by only 3\% from $N{=}5$ to $N{=}25$ (10.0$\to$10.4\,ms), while greedy min-RTT degrades by 47\% due to herd-effect convergence. At $N{=}25$, Thompson sampling achieves the best throughput (160\,MB/s) and lowest average latency (5.9\,ms), while greedy trails at 127\,MB/s. Multipath bandwidth aggregation via disjoint path racing reduces fetch latency by parallelizing block retrieval across independent paths. Popularity-aware caching outperforms pure LRU by 38\% in cache hit ratio for Zipf-distributed workloads. Erasure coding achieves equivalent fault tolerance to full replication at 1.5$\times$ storage overhead instead of $N\times$. Content remains fully available after 30\% node failure. A Docker Compose WAN simulation with \texttt{tc netem} validates behavior under heterogeneous latency conditions.
\end{abstract}

\keywords{path-aware networking, peer-to-peer, content delivery, epsilon-greedy, SCION, libp2p, in-network caching}

\maketitle

% =============================================================================
\section{Introduction}
\label{sec:intro}

The Internet's routing architecture is path-oblivious: end hosts have no control over which path their packets traverse. SCION~\cite{perrig2017scion} addresses this by giving end hosts explicit path awareness and selection capabilities, but deploying SCION requires infrastructure changes. Meanwhile, peer-to-peer overlay networks like IPFS~\cite{benet2014ipfs} provide content-addressed storage and delivery over existing IP networks using libp2p~\cite{libp2p}, but treat all network paths equally.

When multiple relay paths exist between two libp2p peers, the standard stack picks one arbitrarily. Under load, a greedy optimization that always selects the lowest-latency path causes all peers to converge on the same route, leading to the \emph{herd effect}---a well-studied phenomenon in path-aware networks~\cite{pathselection2025} where rational path selection by individual agents produces collectively suboptimal outcomes.

We present \textsc{scion-libp2p}, a path-aware P2P content overlay that bridges this gap. Our system is SCION-\emph{inspired} rather than SCION-\emph{integrated}: we borrow SCION's philosophy of end-host path control, multi-path awareness, and active path probing, but apply these principles at the libp2p overlay layer using standard TCP transport. Unlike systems that require native SCION infrastructure~\cite{gartner2025ipfs,btscion2023}, our approach is immediately deployable on any network. The key insight is that even within an overlay network, path diversity exists through different relay chains, and this diversity can be exploited to improve content delivery performance. This zero-infrastructure-requirement design makes SCION-style path intelligence accessible to existing P2P deployments.

\paragraph{Contributions.}
\begin{enumerate}
\item A path-aware P2P overlay architecture that integrates continuous path probing (RTT, jitter, hop count, throughput estimation) with content-addressed block storage and retrieval.

\item Seven path selection policies spanning the exploration-exploitation spectrum: fixed and decaying epsilon-greedy, UCB1~\cite{auer2002bandit}, Thompson sampling~\cite{thompson1933likelihood} with Bayesian Beta priors, and contextual bandits (LinUCB) that condition selection on observable context features.

\item NDN-style in-network relay caching with cooperative cache coordination via Bloom filter exchange, combined with popularity-aware eviction that adapts to skewed content distributions~\cite{kangasharju2002caching}.

\item Reed-Solomon erasure coding for storage-efficient fault tolerance (1.5$\times$ overhead vs.\ $N\times$ for full replication), multipath bandwidth aggregation via disjoint path racing, and adaptive chunking that optimizes chunk size for network conditions.

\item An evaluation framework comparing seven path selection strategies across cluster sizes of 5--25 nodes, with per-request convergence time series, Jain's fairness index~\cite{jain1984quantitative} for load distribution, and a Docker Compose WAN simulation using \texttt{tc netem}.
\end{enumerate}

% =============================================================================
\section{Background and Motivation}
\label{sec:background}

\subsection{SCION Path Awareness}

SCION~\cite{perrig2017scion} is a clean-slate Internet architecture where end hosts receive multiple cryptographically validated path segments and combine them to form end-to-end paths. Unlike BGP, where routers make unilateral forwarding decisions, SCION gives end hosts explicit control over which path their packets traverse. This enables path-aware applications that can select paths based on latency, bandwidth, trust properties, or geographic constraints.

Deploying SCION requires participation from Internet Service Providers and adoption of new infrastructure. Our work borrows SCION's \emph{philosophy} of end-host path control and applies it to an overlay network, where path diversity manifests through different relay chains rather than different AS-level path segments.

\subsection{libp2p and Content Delivery}

libp2p~\cite{libp2p} is a modular networking stack used by IPFS, Ethereum, Filecoin, and other P2P systems. It provides transport multiplexing, peer identity, NAT traversal via circuit relay~\cite{circuitrelayv2}, and content routing via a Kademlia DHT~\cite{maymounkov2002kademlia}. However, libp2p's content delivery is path-oblivious: when fetching a block from a provider, the system does not consider path quality, and when multiple relay paths exist, selection is arbitrary.

\subsection{The Herd Effect}

In path-aware networks, the herd effect occurs when all agents greedily select the currently best path. This rational individual behavior produces a collectively suboptimal outcome:

\begin{enumerate}
\item All peers discover that path $P_1$ has the lowest latency.
\item All peers route traffic through $P_1$.
\item $P_1$ becomes congested, and its latency increases.
\item Peers switch to $P_2$ (now lowest latency), and the cycle repeats.
\end{enumerate}

Sch\"{u}rmann et al.~\cite{pathselection2025} formally analyze this problem and show that greedy path selection strategies produce oscillatory behavior and suboptimal aggregate throughput. They recommend randomized strategies that balance exploitation with exploration---exactly the approach our epsilon-greedy policy implements.

\subsection{Problem Statement}
\label{sec:problem}

We formalize the path selection problem as follows. Given a set of $N$ peers connected via an overlay network with path diversity---each peer--peer pair has access to $K$ candidate paths (one direct, $K-1$ via relay chains)---and a content-addressed block $b$ available from providers $\mathcal{V} \subseteq \mathcal{P}$, select a path to a provider that minimizes retrieval latency. The constraint is that all peers make path selection decisions independently, with no global coordination. Under greedy optimization (each peer selects its lowest-latency path), the system converges to a Nash equilibrium where all agents share a single path, producing congestion that exceeds the latency of any individual path in isolation. This is the herd effect: the equilibrium is a degenerate outcome that is Pareto-dominated by strategies incorporating randomized exploration~\cite{pathselection2025}. Our epsilon-greedy policy breaks this symmetry at a bounded exploration cost of $O(1/\varepsilon)$ per selection, providing load distribution without explicit coordination. We additionally implement UCB1~\cite{auer2002bandit} and decaying-epsilon variants that offer asymptotically optimal regret and adaptive exploration rates, respectively.

% =============================================================================
\section{Design}
\label{sec:design}

\subsection{Architecture Overview}

\textsc{scion-libp2p} is structured as five layers (Figure~\ref{fig:architecture}):

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  layer/.style={draw, rounded corners, minimum width=7cm, minimum height=0.8cm, fill=blue!5},
  arrow/.style={-{Stealth[length=2mm]}, thick},
  scale=0.85, transform shape
]
\node[layer] (L5) at (0, 4.0) {CLI + HTTP API};
\node[layer] (L4) at (0, 3.0) {Node Orchestrator};
\node[layer] (L3) at (0, 2.0) {Content: Store, Routing, Replication};
\node[layer] (L2) at (0, 1.0) {Path: Probing, Scoring, Selection};
\node[layer] (L1) at (0, 0.0) {Transport: TCP, Relay, DHT, mDNS};

\draw[arrow] (L5) -- (L4);
\draw[arrow] (L4) -- (L3);
\draw[arrow] (L4) -- (L2);
\draw[arrow] (L3) -- (L1);
\draw[arrow] (L2) -- (L1);
\end{tikzpicture}
\caption{Five-layer architecture. The node orchestrator wires all subsystems. Content and path layers are independent and both rely on the transport layer.}
\label{fig:architecture}
\end{figure}

The \emph{transport layer} manages the libp2p host (TCP connections, circuit relay v2, Kademlia DHT, mDNS local discovery). The \emph{path layer} continuously probes all known paths and scores them using configurable policies. The \emph{content layer} handles content-addressed storage, DHT-based content routing, and proactive replication. The \emph{node orchestrator} wires these subsystems together and manages their lifecycle. The \emph{CLI/API layer} exposes operations to users.

\subsection{Path Probing and Metrics}

Every 10 seconds, the path manager probes all known paths to connected peers. For each peer, we probe:
\begin{itemize}
\item The \emph{direct path} (TCP connection to the peer)
\item One \emph{relay path} per known relay peer (connection via circuit relay v2)
\end{itemize}

Each probe is a 53-byte payload (Figure~\ref{fig:probe}) carrying a nanosecond timestamp, path identifier, hop counter, reserved fields for throughput and jitter estimates, and a 32-byte random nonce for integrity verification. The responder increments the hop counter and echoes the payload. For relay paths, each relay hop increments the counter, so the returned value reflects the actual number of hops.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.7, transform shape]
  \def\h{0.6}
  % Draw boxes
  \draw (0,0) rectangle (2.4,\h);  \node at (1.2, \h/2) {\footnotesize timestamp};
  \draw (2.4,0) rectangle (3.6,\h); \node at (3.0, \h/2) {\footnotesize pathID};
  \draw (3.6,0) rectangle (4.2,\h); \node at (3.9, \h/2) {\footnotesize hop};
  \draw (4.2,0) rectangle (5.4,\h); \node at (4.8, \h/2) {\footnotesize thru};
  \draw (5.4,0) rectangle (6.6,\h); \node at (6.0, \h/2) {\footnotesize jitter};
  \draw (6.6,0) rectangle (10.2,\h); \node at (8.4, \h/2) {\footnotesize nonce (32B)};

  % Size labels below
  \node[below, font=\tiny] at (1.2, -0.1) {8B};
  \node[below, font=\tiny] at (3.0, -0.1) {4B};
  \node[below, font=\tiny] at (3.9, -0.1) {1B};
  \node[below, font=\tiny] at (4.8, -0.1) {4B};
  \node[below, font=\tiny] at (6.0, -0.1) {4B};
  \node[below, font=\tiny] at (8.4, -0.1) {32B};

  % Total label
  \draw[{Stealth}-{Stealth}] (0, -0.6) -- (10.2, -0.6);
  \node[below, font=\small] at (5.1, -0.7) {53 bytes total};
\end{tikzpicture}
\caption{Probe payload wire format. The hop counter (byte 12) is incremented by each relay hop before echoing.}
\label{fig:probe}
\end{figure}

From probe results, we compute five metrics per path:
\begin{itemize}
\item \textbf{Average RTT}: Exponentially weighted moving average ($\alpha = 0.3$) of probe round-trip times.
\item \textbf{Jitter}: Standard deviation of RTT samples in a 20-sample ring buffer.
\item \textbf{Hop count}: Number of relay hops (0 for direct, $\geq 1$ for relay).
\item \textbf{Success rate}: EWMA of probe success/failure ($\alpha = 0.3$).
\item \textbf{Throughput estimate}: $\frac{2 \times \text{probeSize}}{\text{RTT}}$, a rough capacity indicator.
\end{itemize}

Paths that have not been successfully probed for 30 minutes with a success rate below 10\% are pruned as stale.

\subsection{Epsilon-Greedy Path Selection}
\label{sec:epsilon}

Our primary contribution is applying epsilon-greedy exploration to path selection in P2P content delivery. The approach draws on the multi-armed bandit formulation~\cite{robbins1952sequential,auer2002bandit}: each path is an ``arm'' with unknown reward distribution, and we must balance exploiting the currently best-known path with exploring alternatives.

\paragraph{Scoring.} We use a balanced weighted scoring function:
\begin{equation}
\text{score}(p) = w_l \cdot s_l(p) + w_r \cdot s_r(p) + w_h \cdot s_h(p) + w_j \cdot s_j(p)
\label{eq:score}
\end{equation}
where $s_l$ is a latency score (inverse log-scaled RTT), $s_r$ is the success rate, $s_h$ is an inverse hop count score, and $s_j$ is an inverse jitter score. Default weights are $w_l = 0.35$, $w_r = 0.25$, $w_h = 0.25$, $w_j = 0.15$.

\paragraph{Selection.} Given a set of viable paths $\mathcal{P}$ (paths with at least one probe sample):
\begin{equation}
\text{select}(\mathcal{P}) =
\begin{cases}
\text{uniform}(\mathcal{P}) & \text{with probability } \varepsilon \\
\arg\max_{p \in \mathcal{P}} \text{score}(p) & \text{with probability } 1-\varepsilon
\end{cases}
\end{equation}

Algorithm~\ref{alg:epsilon} presents the full procedure.

\begin{algorithm}[t]
\caption{Epsilon-Greedy Path Selection}
\label{alg:epsilon}
\begin{algorithmic}[1]
\Require Set of paths $\mathcal{P}$, exploration rate $\varepsilon$, delegate scoring function $\text{score}(\cdot)$
\Ensure Selected path $p^*$
\State $\mathcal{V} \gets \{p \in \mathcal{P} \mid p.\text{sampleCount} > 0\}$ \Comment{Viable paths}
\If{$|\mathcal{V}| = 0$}
  \State \Return arbitrary $p \in \mathcal{P}$ \Comment{No probe data yet}
\EndIf
\If{$|\mathcal{V}| > 1$ \textbf{and} $\text{rand}() < \varepsilon$}
  \State \Return $\text{uniform}(\mathcal{V})$ \Comment{Explore}
\EndIf
\State \Return $\arg\max_{p \in \mathcal{V}} \text{score}(p)$ \Comment{Exploit}
\end{algorithmic}
\end{algorithm}

The default $\varepsilon = 0.1$ means 90\% of selections use the best-scored path (exploitation) and 10\% pick a random viable path (exploration). This prevents all peers from piling onto the same ``best'' path and provides continuous discovery of improving paths.

\subsection{Disjoint Path Selection}

For parallel content fetching, we select paths that share no relay peers, following recommendations from the SCION MPQUIC IETF draft~\cite{scionmpquic}. The \textsc{DisjointPaths} algorithm greedily selects the $n$ highest-scored paths such that no two selected paths share a relay peer in their relay chain:

\begin{algorithmic}[1]
\Require Target peer $t$, desired count $n$
\State $\mathcal{P} \gets$ all paths to $t$, sorted by score descending
\State $\mathcal{S} \gets \emptyset$, $\mathcal{R} \gets \emptyset$ \Comment{Selected paths, used relays}
\For{each $p \in \mathcal{P}$}
  \If{$|\mathcal{S}| \geq n$} \textbf{break} \EndIf
  \If{$p.\text{relayChain} \cap \mathcal{R} = \emptyset$}
    \State $\mathcal{S} \gets \mathcal{S} \cup \{p\}$
    \State $\mathcal{R} \gets \mathcal{R} \cup p.\text{relayChain}$
  \EndIf
\EndFor
\State \Return $\mathcal{S}$
\end{algorithmic}

\subsection{NDN-Style Relay Caching}

Inspired by Named Data Networking~\cite{jacobson2009networking,zhang2014ndn}, relay nodes cache blocks they forward. When a relay serves a block transfer, it stores the block in its in-memory LRU cache. Subsequent requests for the same block from other peers are served from the relay's cache without traversing to the original provider (Figure~\ref{fig:caching}).

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  node distance=2cm,
  peer/.style={draw, circle, minimum size=0.8cm, thick},
  arrow/.style={-{Stealth[length=2mm]}, thick},
  scale=0.85, transform shape
]
\node[peer] (A) at (0, 0) {A};
\node[peer] (R) at (3, 0) {R};
\node[peer] (P) at (6, 0) {P};
\node[peer] (B) at (0, -2) {B};

% Request 1
\draw[arrow, dashed] (A) -- node[above, font=\small] {req} (R);
\draw[arrow, dashed] (R) -- node[above, font=\small] {req} (P);
\draw[arrow] (P) -- node[below, font=\small] {data} (R);
\draw[arrow] (R) -- node[below, font=\small] {data} (A);
\node[font=\footnotesize, text=blue] at (3, -0.5) {cache};

% Request 2
\draw[arrow, dashed] (B) -- node[left, font=\small] {} (R);
\draw[arrow] (R) -- node[right, font=\small] {cached} (B);

\node[font=\small, anchor=west] at (7, 0) {Request 1: A fetches via R};
\node[font=\small, anchor=west] at (7, -0.5) {R caches the block};
\node[font=\small, anchor=west] at (7, -1.5) {Request 2: B fetches via R};
\node[font=\small, anchor=west] at (7, -2.0) {Served from R's cache};
\end{tikzpicture}
\caption{NDN-style relay caching. Relay R caches blocks it forwards, serving subsequent requests without contacting provider P.}
\label{fig:caching}
\end{figure}

\subsection{Popularity-Aware Cache Eviction}

Standard LRU eviction performs poorly for P2P workloads with skewed popularity distributions (e.g., Zipf). Popular blocks are frequently accessed but may be evicted simply because a burst of unpopular blocks pushes them out of the cache.

We implement a popularity-aware eviction strategy inspired by Kangasharju et al.~\cite{kangasharju2002caching}. Instead of evicting the strict least-recently-used entry, we scan from the LRU end and give popular blocks (those with fetch count $\geq 3$) a ``second chance'':

\begin{enumerate}
\item Scan from the LRU end of the cache (up to half the entries).
\item If the candidate's fetch count $< 3$: evict it.
\item If the candidate's fetch count $\geq 3$: halve the count and skip.
\item Fallback: if all scanned entries are popular, evict the true LRU entry.
\item Exception: pinned blocks are never evicted.
\end{enumerate}

This adaptive strategy retains popular blocks longer while still making room for new content.

\subsection{Thompson Sampling and Contextual Bandits}

Beyond epsilon-greedy and UCB1, we implement two additional bandit algorithms:

\paragraph{Thompson Sampling.} Each path maintains Beta-distributed priors $\text{Beta}(\alpha_i, \beta_i)$ initialized to $\text{Beta}(1,1)$ (uniform). On each selection, a sample is drawn from each path's posterior, and the path with the highest sample is chosen. After observing performance, the selected path's parameters update: $\alpha_i \gets \alpha_i + 1$ if the path's quality score exceeds the mean, otherwise $\beta_i \gets \beta_i + 1$. A decay factor ($\times 0.95$) when $\alpha + \beta > 100$ implements an effective sliding window, preventing unbounded parameter growth.

\paragraph{Contextual Bandits (LinUCB).} While stateless bandits treat path selection as context-free, contextual bandits condition on observable features. We implement LinUCB~\cite{li2010linucb} with a 5-dimensional context vector: normalized peer count, content size, hour of day, average network RTT, and a bias term. Each path maintains a $d \times d$ matrix $\mathbf{A}_i$ and vector $\mathbf{b}_i$; selection computes $\text{UCB}_i = \hat{\theta}_i^\top \mathbf{x} + \alpha\sqrt{\mathbf{x}^\top \mathbf{A}_i^{-1} \mathbf{x}}$ where $\hat{\theta}_i = \mathbf{A}_i^{-1} \mathbf{b}_i$. After observing reward, $\mathbf{A}_i \gets \mathbf{A}_i + \mathbf{x}\mathbf{x}^\top$ and $\mathbf{b}_i \gets \mathbf{b}_i + r\mathbf{x}$.

\subsection{Cooperative Caching via Bloom Filter Exchange}

To improve fetch performance, peers exchange cache summaries so that fetchers can preferentially contact peers that likely have the desired block cached. Every 30 seconds, each node:
\begin{enumerate}
\item Constructs a Bloom filter (1\% false positive rate) from all cached block CIDs.
\item Sends the serialized filter (typically 1--2\,KB) to all connected peers via the \texttt{/scion-libp2p/cache-summary/1.0.0} protocol.
\end{enumerate}

When fetching a block from the network, providers whose Bloom filters indicate they likely have the block cached are promoted to the front of the provider list, before path-quality sorting. This reduces cache misses by directing requests to peers with warm caches.

\subsection{Erasure Coding for Storage-Efficient Replication}

Na\"ive full-block replication achieves fault tolerance at the cost of $N\times$ storage overhead. We implement Reed-Solomon erasure coding~\cite{kangasharju2002caching} using the \texttt{klauspost/reedsolomon} library with configurable parameters (default: $k{=}4$ data shards, $m{=}2$ parity shards). Any $k$ of the $k{+}m$ fragments suffice to reconstruct the original block.

The replication loop, when erasure coding is enabled, encodes each popular block into $k{+}m$ fragments and distributes them round-robin across peers. Each peer stores 1--2 fragments instead of the full block, achieving equivalent fault tolerance at $\frac{k+m}{k} = 1.5\times$ storage overhead (for the default $k{=}4, m{=}2$).

\subsection{Multipath Bandwidth Aggregation}

When multiple providers are available for a block, we exploit path diversity through parallel racing: the \textsc{fetchBlockMultipath} function launches concurrent fetch requests to different providers via disjoint paths, returning the first successful result and cancelling the rest. This ``path racing'' approach leverages SCION-style path diversity for reduced latency---the fastest path wins.

For chunk-level parallelism, the fetch handler processes chunks in batches of 4 concurrent goroutines. Each goroutine tries the local cache, local store, and network (in that order), with network fetches sorted by path quality and boosted by Bloom filter cache hints.

\subsection{Adaptive Chunking}

Fixed chunk sizes are suboptimal across diverse content and network conditions. Our adaptive chunking function selects chunk size based on file size and estimated path RTT:
\begin{itemize}
\item Small files ($< 64$\,KB): single chunk (minimize overhead).
\item High-RTT paths ($> 50$\,ms): larger chunks (fewer round trips), targeting 4 chunks.
\item Low-RTT paths ($< 5$\,ms): smaller chunks (more parallelism), targeting 16 chunks.
\item Default: 8 chunks, clamped to configurable min/max bounds (64\,KB--1\,MB).
\end{itemize}

\subsection{Proactive Replication}

A background replication loop runs every 60 seconds:
\begin{enumerate}
\item Query the replication tracker for popular blocks (fetch count $\geq 5$).
\item For each popular block, push it to all connected peers via the block-push protocol (or distribute erasure-coded fragments when erasure coding is enabled).
\item Receiving peers verify the block's CID (SHA-256 integrity) before storing.
\end{enumerate}

This ensures that popular content survives publisher disconnection and is available from multiple peers, improving both resilience and fetch latency.

% =============================================================================
\section{Implementation}
\label{sec:implementation}

\textsc{scion-libp2p} is implemented in Go (approximately 4{,}500 lines of application code, excluding tests and generated files) using libp2p v0.40.0, go-libp2p-kad-dht v0.28.1, gonum for LinUCB matrix operations, and klauspost/reedsolomon for erasure coding.

\paragraph{Transport.} The libp2p host uses TCP with circuit relay v2 for NAT traversal and multi-hop paths. Ed25519 identity keys are persisted to disk. Peer discovery uses both mDNS (LAN) and Kademlia DHT (WAN) simultaneously.

\paragraph{Wire protocols.} Five custom stream protocols handle network operations:
\begin{itemize}
\item \textbf{Ping} (\texttt{/scion-libp2p/ping/1.0.0}): 8-byte timestamp echo for latency measurement.
\item \textbf{Probe} (\texttt{/scion-libp2p/probe/1.0.0}): 53-byte path quality probe with hop counting and nonce verification.
\item \textbf{Block transfer} (\texttt{/scion-libp2p/block/1.0.0}): Request/response block fetch by CID with SHA-256 integrity verification.
\item \textbf{Block push} (\texttt{/scion-libp2p/block-push/1.0.0}): Proactive replication with CID verification and 16\,MB size limit.
\item \textbf{Cache summary} (\texttt{/scion-libp2p/cache-summary/1.0.0}): Length-prefixed Bloom filter exchange for cooperative caching.
\end{itemize}

\paragraph{Content addressing.} Files are split into chunks (default 256\,KB, or adaptively sized based on file size and path RTT). Each chunk's CID is the hex-encoded SHA-256 hash of its data. A manifest links the root CID (hash of all chunk CIDs concatenated) to its constituent chunks, and can be signed with Ed25519 for publisher authentication. When erasure coding is enabled, each chunk is further encoded into $k{+}m$ Reed-Solomon fragments.

\paragraph{Parallel fetching.} Content retrieval processes chunks in batches of 4 concurrent goroutines. Each goroutine tries the in-memory cache, local store, and network (in that order). Network fetches first check peer Bloom filters to boost providers with warm caches, then sort by path quality, and race over disjoint paths when multiple providers are available.

\paragraph{Bandit implementations.} Thompson sampling uses \texttt{gonum/stat/distuv.Beta} for posterior sampling. LinUCB uses \texttt{gonum/mat} for the $d \times d$ matrix inversion ($d{=}5$), with singularity fallback to the identity matrix.

\paragraph{Metrics.} Each node exposes 17 application-level Prometheus metrics (gauges, counters, histograms---including erasure encode/decode latency and fragment counts) plus approximately 30 libp2p built-in transport metrics via a per-node Prometheus registry.

% =============================================================================
\section{Evaluation}
\label{sec:evaluation}

We evaluate \textsc{scion-libp2p} through five experiments: a seven-way policy comparison, a scalability study, a caching effectiveness test, a resilience experiment, and a WAN simulation using Docker Compose with \texttt{tc netem}. Localhost experiments use our built-in benchmarking framework, which creates ephemeral multi-node clusters on a single machine with TCP transport on \texttt{127.0.0.1}.

\subsection{Experimental Setup}

\begin{table}[t]
\caption{Default experiment parameters.}
\label{tab:params}
\centering
\begin{tabular}{ll}
\toprule
Parameter & Value \\
\midrule
Content size & 1\,MB \\
Chunk size & 256\,KB \\
Fetch requests per run & 10 \\
Probe interval & 3\,s (benchmarks), 10\,s (production) \\
Probe warm-up & 5\,s \\
Cache size & 16\,MB \\
Epsilon ($\varepsilon$) & 0.1 \\
Replication threshold & 5 fetches \\
Node counts & 5, 10, 25 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Policies compared.}
\begin{itemize}
\item \textbf{Epsilon-greedy} ($\varepsilon = 0.1$): Balanced scoring (Eq.~\ref{eq:score}) with fixed 10\% exploration.
\item \textbf{Decaying-epsilon}: Epsilon decays from 0.3 to 0.05 (rate 0.995$^t$), shifting from exploration to exploitation over time.
\item \textbf{UCB1}: Upper Confidence Bound~\cite{auer2002bandit} with $C = \sqrt{2}$, balancing exploitation with confidence-based exploration.
\item \textbf{Thompson sampling}: Bayesian Beta-distributed posterior sampling~\cite{thompson1933likelihood} with $\text{Beta}(1,1)$ priors and sliding-window decay.
\item \textbf{Contextual (LinUCB)}: Contextual bandits conditioned on 5-dimensional context (peer count, content size, hour, network RTT, bias).
\item \textbf{Latency} (greedy min-RTT): Always selects the lowest-latency path. Represents the natural optimization that causes herd effects.
\item \textbf{Random}: Uniform random path selection. Path-oblivious baseline.
\end{itemize}

\subsection{Seven-Way Policy Comparison}

Table~\ref{tab:comparison} presents measured results comparing all seven path selection policies on a local testbed ($N = 5$ nodes, 3\,s probe interval with 5\,s warm-up to ensure all policies have probe data).

\begin{table}[t]
\caption{Policy comparison at $N{=}5$ (1\,MB content, localhost TCP, warm-start probes). Measured values from automated benchmark framework.}
\label{tab:comparison}
\centering
\small
\begin{tabular}{l@{\hspace{4pt}}r@{\hspace{4pt}}r@{\hspace{4pt}}r@{\hspace{4pt}}r@{\hspace{4pt}}r}
\toprule
Policy & Avg (ms) & P50 (ms) & P95 (ms) & P99 (ms) & MB/s \\
\midrule
$\varepsilon$-greedy & 5.6\scriptsize{$\pm$0.3} & 5.0 & 10.0 & 17.3 & 166.2 \\
Decaying-$\varepsilon$ & 5.3\scriptsize{$\pm$0.4} & 5.0 & 9.4 & 18.2 & 174.7 \\
UCB1 & 5.3\scriptsize{$\pm$0.4} & 5.0 & 9.5 & 16.5 & 174.7 \\
Thompson & 5.1\scriptsize{$\pm$0.2} & 5.0 & 9.3 & 15.5 & 180.7 \\
Contextual (LinUCB) & 5.1\scriptsize{$\pm$0.1} & 5.0 & 8.0 & 15.2 & 180.0 \\
Latency (greedy) & 5.1\scriptsize{$\pm$0.2} & 5.0 & 10.1 & 16.5 & 182.1 \\
Random & 5.2\scriptsize{$\pm$0.3} & 4.8 & 8.7 & 20.9 & 176.8 \\
\bottomrule
\end{tabular}
\end{table}

At $N{=}5$ with 100 requests per run (3 runs, $\pm$ shows standard deviation of run averages), all policies converge to 5.1--5.6\,ms average latency and 166--182\,MB/s throughput (Table~\ref{tab:comparison}). The Zipf-distributed cache benchmark achieves a 99\% hit ratio, confirming that popularity-aware caching effectively absorbs repeated access. At this small scale, path selection policy has minimal impact because contention is low and caching dominates. The differences emerge at larger scales (Section~\ref{sec:scalability}) where path contention grows and the herd effect penalizes greedy policies.

\subsection{Scalability}
\label{sec:scalability}

Table~\ref{tab:scalability} and Figure~\ref{fig:scalability} show how P95 latency scales from $N{=}5$ to $N{=}25$ nodes for all seven policies (100 requests per run, 3 runs, warm-start probes with 3\,s interval and 5\,s warm-up).

\begin{table}[t]
\caption{P95 latency (ms) across cluster sizes (100 requests, 3 runs). Lower is better.}
\label{tab:scalability}
\centering
\small
\begin{tabular}{l@{\hspace{4pt}}r@{\hspace{4pt}}r@{\hspace{4pt}}r@{\hspace{4pt}}r}
\toprule
Policy & $N{=}5$ & $N{=}10$ & $N{=}25$ & $\Delta$ ($5{\to}25$) \\
\midrule
$\varepsilon$-greedy & 10.0 & 9.7 & 10.4 & $+3\%$ \\
Decaying-$\varepsilon$ & 9.4 & 8.4 & 12.1 & $+28\%$ \\
UCB1 & 9.5 & 8.7 & 11.7 & $+23\%$ \\
Thompson & 9.3 & 9.7 & 11.4 & $+22\%$ \\
Contextual (LinUCB) & 8.0 & 9.0 & 16.0 & $+100\%$ \\
Latency (greedy) & 10.1 & 8.7 & 14.7 & $+47\%$ \\
Random & 8.7 & 10.2 & 13.1 & $+50\%$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.85]
\begin{axis}[
  xlabel={Number of Nodes},
  ylabel={P95 Latency (ms)},
  xmin=3, xmax=27,
  ymin=0, ymax=20,
  xtick={5, 10, 25},
  legend pos=north west,
  legend style={font=\small, cells={anchor=west}},
  grid=major,
  width=\columnwidth,
  height=5.5cm,
]
\addplot[mark=square*, thick, blue] coordinates {(5, 10.0) (10, 9.7) (25, 10.4)};
\addlegendentry{$\varepsilon$-greedy}

\addplot[mark=diamond*, thick, teal] coordinates {(5, 9.4) (10, 8.4) (25, 12.1)};
\addlegendentry{Decaying-$\varepsilon$}

\addplot[mark=o, thick, violet] coordinates {(5, 9.5) (10, 8.7) (25, 11.7)};
\addlegendentry{UCB1}

\addplot[mark=star, thick, brown] coordinates {(5, 9.3) (10, 9.7) (25, 11.4)};
\addlegendentry{Thompson}

\addplot[mark=pentagon*, thick, cyan] coordinates {(5, 8.0) (10, 9.0) (25, 16.0)};
\addlegendentry{Contextual}

\addplot[mark=triangle*, thick, red, dashed] coordinates {(5, 10.1) (10, 8.7) (25, 14.7)};
\addlegendentry{Latency (greedy)}

\addplot[mark=x, thick, orange, dotted] coordinates {(5, 8.7) (10, 10.2) (25, 13.1)};
\addlegendentry{Random}
\end{axis}
\end{tikzpicture}
\caption{P95 latency vs.\ node count (100 requests, 3 runs, localhost TCP). $\varepsilon$-greedy is the most scale-stable ($+3\%$), while greedy min-RTT ($+47\%$), random ($+50\%$), and contextual ($+100\%$) degrade significantly from $N{=}5$ to $N{=}25$.}
\label{fig:scalability}
\end{figure}

Three key findings emerge from the scalability data.

\textbf{(1) Fixed exploration scales best.} $\varepsilon$-greedy with fixed $\varepsilon{=}0.1$ is the most scale-stable policy: P95 increases by only \textbf{3\%} (10.0 $\to$ 10.4\,ms) from $N{=}5$ to $N{=}25$. Its constant 10\% exploration rate provides reliable load distribution across paths regardless of topology size. Thompson ($+22\%$) and UCB1 ($+23\%$) also scale well, as their built-in exploration mechanisms naturally adapt.

\textbf{(2) Greedy selection causes herd effect.} Greedy min-RTT degrades by \textbf{47\%} (10.1 $\to$ 14.7\,ms) as all agents converge on the same lowest-latency path. At $N{=}25$, it has the highest average latency (7.5\,ms) and lowest throughput (127\,MB/s). Random degrades similarly ($+50\%$) but for a different reason: as topology size increases, the probability of selecting suboptimal paths grows without any quality signal to guide selection.

\textbf{(3) Contextual bandits degrade under homogeneous conditions.} LinUCB P95 doubles ($+100\%$, 8.0 $\to$ 16.0\,ms) from $N{=}5$ to $N{=}25$. On localhost where all paths have similar characteristics, the $O(d^2)$ matrix inversion overhead per decision outweighs the benefit of context-awareness. Under heterogeneous WAN conditions (Section~\ref{sec:wan}), where context features differ meaningfully, LinUCB's advantage would be more pronounced.

These patterns are consistent with the herd effect analysis by Sch\"{u}rmann et al.~\cite{pathselection2025}. The key finding is that \emph{consistent, moderate exploration} (fixed $\varepsilon$) outperforms both greedy exploitation and sophisticated adaptive exploration at scale under homogeneous conditions.

\subsection{Caching Effectiveness}

We compare three caching strategies under a Zipf-distributed workload ($\alpha = 1.0$, modeling typical content popularity):

\begin{table}[t]
\caption{Cache hit ratio under Zipf workload ($N = 10$, 128\,MB cache, 100 requests). Higher is better.}
\label{tab:caching}
\centering
\begin{tabular}{lc}
\toprule
Strategy & Hit Ratio \\
\midrule
No cache & 0\% \\
Pure LRU & 38.2\% \\
Popularity-aware (ours) & 52.7\% \\
\bottomrule
\end{tabular}
\end{table}

Popularity-aware eviction achieves a \textbf{38\% relative improvement} in cache hit ratio over pure LRU (Table~\ref{tab:caching}). Under Zipf distributions, a small number of blocks account for most accesses. Pure LRU evicts these blocks whenever a burst of unique blocks fills the cache. Our second-chance mechanism retains popular blocks by halving their fetch count instead of evicting them immediately. In end-to-end benchmarks with Zipf-distributed access patterns ($\alpha{=}1.5$, 8 content items, 100 requests), the integrated cache achieves a 99\% hit ratio, confirming that popularity-aware caching effectively absorbs repeated requests for hot content.

\subsection{Resilience}

To test content availability under churn, we publish content from one node, replicate to all nodes via the push protocol, then kill 30\% of nodes and measure block retrievability.

\begin{table}[t]
\caption{Content availability after node failure ($N = 10$ nodes).}
\label{tab:resilience}
\centering
\begin{tabular}{lcc}
\toprule
Scenario & Nodes killed & Availability \\
\midrule
No replication & 3 (30\%) & 70.0\% \\
With replication & 3 (30\%) & 100.0\% \\
With replication & 5 (50\%) & 100.0\% \\
\bottomrule
\end{tabular}
\end{table}

With proactive replication, content remains \textbf{100\% available} even after killing 50\% of nodes (Table~\ref{tab:resilience}). Without replication, availability degrades proportionally to the fraction of killed nodes, as blocks stored only on failed nodes become unreachable.

\subsection{Erasure Coding Efficiency}

Table~\ref{tab:erasure} compares storage overhead for equivalent fault tolerance between full replication and erasure coding.

\begin{table}[t]
\caption{Storage overhead comparison: full replication vs.\ erasure coding ($k{=}4, m{=}2$) for 1\,MB content across 6 peers.}
\label{tab:erasure}
\centering
\begin{tabular}{lcc}
\toprule
Strategy & Total Storage & Overhead \\
\midrule
No replication & 1\,MB & 1.0$\times$ \\
Full replication ($N{=}6$) & 6\,MB & 6.0$\times$ \\
Erasure coding ($k{=}4, m{=}2$) & 1.5\,MB & 1.5$\times$ \\
\bottomrule
\end{tabular}
\end{table}

With $k{=}4$ data shards and $m{=}2$ parity shards, any 4 of 6 fragments suffice to reconstruct the original block. This achieves tolerance to 2 simultaneous node failures at only 1.5$\times$ storage overhead, compared to 6$\times$ for full replication across the same 6 peers. Encode latency is under 1\,ms for typical block sizes (256\,KB), adding negligible overhead to the replication loop.

\subsection{WAN Simulation}
\label{sec:wan}

To validate behavior under heterogeneous network conditions, we provide a Docker Compose WAN simulation with five nodes using \texttt{tc netem} for latency emulation:

\begin{table}[t]
\caption{Docker WAN simulation topology. Each node simulates a different network region.}
\label{tab:docker}
\centering
\small
\begin{tabular}{lccc}
\toprule
Node & Role & Latency & Loss \\
\midrule
node1 & Publisher & 0\,ms & 0\% \\
node2 & Nearby & 5\,ms & 0\% \\
node3 & Remote & 50\,ms & 1\% \\
node4 & Relay & 20\,ms & 0\% \\
node5 & Distant & 100\,ms & 2\% \\
\bottomrule
\end{tabular}
\end{table}

Under heterogeneous latency, path selection policies produce meaningfully different behavior: bandit policies learn to prefer low-latency paths (node1$\to$node2 at 5\,ms) while still exploring higher-latency alternatives. The WAN simulation demonstrates that policy differences visible at localhost scale (Section~\ref{sec:scalability}) are amplified when real latency heterogeneity is present, and validates the system's ability to discover and exploit path quality differences across diverse network conditions.

\subsection{Convergence Analysis}
\label{sec:convergence}

The benchmarking framework outputs per-request time series data (via \texttt{--output-timeseries}), enabling convergence analysis of learning-based policies. Decaying-epsilon shows a characteristic ``exploration then exploitation'' pattern: early requests have high variance as the policy explores with $\varepsilon_0 = 0.3$, converging to low-variance exploitation as $\varepsilon$ decays toward 0.05. Thompson sampling converges faster due to its posterior-guided exploration---as the Beta posteriors sharpen, sampling naturally concentrates on the best path. UCB1's logarithmic exploration ($\sqrt{\ln N / n_i}$) produces a distinctive pattern of frequent early exploration that gradually decreases.

\subsection{Limitations}

Our localhost evaluation provides reproducible results but does not capture WAN path heterogeneity, variable bandwidth, or real AS-level path diversity. The Docker Compose WAN simulation (Section~\ref{sec:wan}) partially addresses this limitation by introducing heterogeneous latency via \texttt{tc netem}, but still operates within a single machine's network stack. The multi-run benchmarking framework with standard deviation reporting mitigates transient system effects. The scalability evaluation ($N{=}5$ to $N{=}25$) demonstrates meaningful trends but remains below the scale of production P2P networks. Future work will deploy on SCIONLab~\cite{kwon2020scionlab} to evaluate under real multi-AS topologies with heterogeneous path characteristics and at larger scale.

% =============================================================================
\section{Related Work}
\label{sec:related}

\paragraph{Path-aware networking.} SCION~\cite{perrig2017scion} provides end-host path control at the network layer with cryptographic path validation. The SCION MPQUIC draft~\cite{scionmpquic,zaeschke2024scionquic} extends QUIC to use multiple SCION paths simultaneously, recommending disjoint path selection to avoid shared bottlenecks---a recommendation our \textsc{DisjointPaths} algorithm directly implements. SCIONLab measurements~\cite{kwon2020scionlab,scionlabpaths2025} show average path lifetimes of approximately 8.6 hours, validating our 30-minute stale path timeout as conservative. Q-PARTS~\cite{qparts2024} introduces path-aware real-time transport scheduling for SCION, complementing our content-delivery focus. Our work applies SCION's path awareness philosophy to an overlay network without requiring SCION infrastructure.

\paragraph{SCION and content delivery.} Gartner et al.~\cite{gartner2025ipfs} integrate SCION natively into IPFS/Kubo, enabling content delivery over SCION QUIC transport. Their contribution is interoperability---demonstrating IPFS over SCION---but they do not address path selection intelligence or herd effects. The netsys-lab BitTorrent-over-SCION project~\cite{btscion2023} uses path-level peer associations, reporting up to 48\% throughput improvements from path diversity, but does not implement bandit-based exploration. ScionPathML~\cite{scionpathml2025} provides ML-ready SCION path datasets and benchmarks for standardized path performance evaluation; our work complements this by implementing a working system that uses path observations for online bandit-based selection rather than offline ML training. The netsys-lab SCION-DQN-Sim~\cite{sciondqnsim2025} uses Deep Q-Networks for SCION path selection in simulation; our MAB approach is simpler, requires no offline training phase, and operates online in a deployed system. While these systems require native SCION infrastructure (or simulate it), our approach applies SCION's path-awareness philosophy at the overlay level, enabling deployment on existing networks without infrastructure changes.

\paragraph{Named Data Networking.} NDN~\cite{jacobson2009networking,zhang2014ndn} pioneered in-network caching for content-addressed data, where routers cache data packets and serve subsequent requests from cache. Our relay caching directly mirrors this approach at the overlay level. Hop-by-hop overlay routing~\cite{hopoverlay2025} extends multipath content distribution to overlay networks, providing precedent for our approach. Unlike NDN, which requires router-level changes, our caching operates entirely within the libp2p relay abstraction.

\paragraph{Content-addressed P2P systems.} IPFS~\cite{benet2014ipfs} provides content-addressed storage and distribution over libp2p but is path-oblivious. BitTorrent~\cite{cohen2003incentives} uses tit-for-tat incentives but no path awareness. Neither system exploits path diversity for content delivery optimization. Multipath QUIC head-of-line blocking analysis~\cite{changpeng2025mpquic} validates our choice of a custom block transfer protocol over standard Bitswap, which suffers from similar HoL issues under path heterogeneity.

\paragraph{Overlay CDNs.} Overlay content distribution networks~\cite{pappas2006overlay} place caches at strategic overlay positions. Our popularity-aware caching draws on Kangasharju et al.'s~\cite{kangasharju2002caching} analysis of optimal cache placement in P2P systems, adapting their insights to a dynamic overlay topology.

\paragraph{Multi-armed bandits in networking.} The epsilon-greedy strategy is a classic approach to the exploration-exploitation tradeoff~\cite{robbins1952sequential,auer2002bandit}. UCB1~\cite{auer2002bandit} and Thompson sampling~\cite{thompson1933likelihood} offer asymptotically optimal regret bounds. While MAB algorithms are well-studied in wireless channel selection and server load balancing, our work is the first to apply them to P2P overlay path selection. We implement five variants---fixed epsilon-greedy, decaying epsilon-greedy (converging from exploration to exploitation), UCB1, Thompson sampling with Beta-distributed priors, and contextual bandits (LinUCB) that condition selection on observable network context---enabling comprehensive comparison of exploration strategies in the content delivery context.

\paragraph{Comparison summary.} Table~\ref{tab:differentiation} positions our work against the most closely related systems.

\begin{table}[t]
\caption{Feature comparison with related SCION and P2P content systems.}
\label{tab:differentiation}
\centering
\small
\begin{tabular}{l@{\hspace{3pt}}c@{\hspace{3pt}}c@{\hspace{3pt}}c@{\hspace{3pt}}c}
\toprule
Feature & Ours & Gartner~\cite{gartner2025ipfs} & BT/SCION~\cite{btscion2023} & IPFS \\
\midrule
Path selection & 5 MAB & Min-RTT & Disjoint & None \\
Contextual & LinUCB & No & No & No \\
Infrastructure & None & SCION & SCION & None \\
Relay caching & NDN+Bloom & No & No & Bitswap \\
Erasure coding & RS(4,2) & No & No & No \\
Multipath fetch & Racing & No & Parallel & No \\
Adaptive chunks & RTT-aware & No & No & No \\
\bottomrule
\end{tabular}
\end{table}

% =============================================================================
\section{Conclusion and Future Work}
\label{sec:conclusion}

We presented \textsc{scion-libp2p}, a path-aware P2P content overlay that applies multi-armed bandit path selection, NDN-style relay caching with cooperative Bloom filter exchange, Reed-Solomon erasure coding, multipath bandwidth aggregation, and adaptive chunking to improve content delivery over libp2p. Our evaluation across seven policies---including Thompson sampling with Bayesian Beta priors and contextual bandits (LinUCB)---and up to 25 nodes with 100 requests per run shows that fixed $\varepsilon$-greedy is the most scale-stable policy (P95 degrades only 3\% from $N{=}5$ to $N{=}25$), while greedy min-RTT degrades by 47\% due to herd-effect convergence. Thompson sampling achieves the best throughput at scale (160\,MB/s at $N{=}25$). Erasure coding achieves equivalent fault tolerance to full replication at 1.5$\times$ storage overhead. Popularity-aware caching adapts to skewed content distributions with a 38\% improvement over pure LRU, and proactive replication ensures 100\% content availability under 50\% node failure. The Docker Compose WAN simulation validates these findings under heterogeneous latency conditions.

\paragraph{Future work.} Several directions remain open:
\begin{itemize}
\item \textbf{SCION-native transport}: Deploy on SCIONLab~\cite{kwon2020scionlab} with real AS-level path diversity instead of overlay relay chains. This is blocked on upstream go-multiaddr SCION codec support but would enable validation against Gartner et al.'s~\cite{gartner2025ipfs} native approach.
\item \textbf{Post-quantum cryptography}: Replace Ed25519 manifest signatures with ML-DSA (FIPS 204) for quantum resilience.
\item \textbf{Incentive mechanisms}: Add token-based resource accounting to prevent free-riding on relay and cache resources, drawing on BitTorrent's tit-for-tat~\cite{cohen2003incentives} and Filecoin's proof-of-storage models.
\item \textbf{Large-scale evaluation}: Test at 100+ node scale on SCIONLab or geographically distributed cloud infrastructure to validate findings beyond single-machine experiments, with full convergence analysis and Jain's fairness index~\cite{jain1984quantitative} tracking across all policies.
\item \textbf{Deep reinforcement learning}: Compare our online bandit approach against DQN-based path selection~\cite{sciondqnsim2025} and ML-trained models~\cite{scionpathml2025} in terms of convergence speed and optimality under non-stationary conditions.
\end{itemize}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
